An exploratory analysis of the influence of resource use on the yield verse quality trade-off in Australian vineyards

### 2023-08-01 article.tex
discussion edits!

The most determining factor in the output quality and yield of a vineyard was size. There was a strong relationship between size and resource use, in that the overall space of a vineyard and its access to resources determined the upper limit of potential yield. However, size was also inversely related to the potential quality, with higher quality being related more to high resource inputs per area than overall access to resources. These effects were augmented by regional and yearly affects. Even given regional and yearly changes, there was a strong sense of smaller vineyards being easier to manage and ensure high quality when compared to larger vineyards.

@@

Literature shows that there are many on-the-ground decisions that influence both quality and yield. These decisions are governed by complex physical and social forces such as international market demands, disease pressures and natural disasters \citep{abadCoverCropsViticulture2021,cortezUsingDataMining2009,hallWithinseasonTemporalVariation2011,i.goodwinManagingSoilWater2009,kasimatiPredictingGrapeSugar2022,oliverReviewSoilPhysical2013,srivastavaNondestructiveSensingMethods2018}; with many of these occurrences being highlighted throughout the past decades vintage reports \citep{wineaustraliaNationalVintageReport2019,wineaustraliaNationalVintageReport2021,wineaustraliaNationalVintageReport2022,winemakersfederationofaustraliaNationalVintageReport2013,winemakersfederationofaustraliaNationalVintageReport2014,winemakersfederationofaustraliaNationalVintageReport2015,winemakersfederationofaustraliaNationalVintageReport2016,winemakersfederationofaustraliaNationalVintageReport2017,winemakersfederationofaustraliaNationalVintageReport2018}.
 %This definitely needs to be broken up, what were these occurences, which year was significant for what?
It is also important to consider that these reports show that the warm inland regions have seen a decline in profit during this period, as they were often compared to other regions that focused more on quality than quantity. This is an important consideration, as the size of some of these vineyards and resultant capactiy to produce greater volumnes would only require only a minor increase to sale price to out compete other regions. It is important to consider the unique challenges of winegrwoing when compared to other agricultural industries, as vineyards are vertically integrated within the wine industry; tying them to secondary and tertiary industries, such as wine production, packaging, transport and sales. This results in unique issues and considerations for each vineyard, where on-the-ground decisions are influenced by other wine industry's choices, such as the use of sustainable practices in vineyards as a requirement for sale in overseas markets; notably these interactions can be further complicated by some winegrowers being completely integrated into a wine company, while others are not\citep{knightFirmResourcesDevelopment2019}. Incorporating decisions into the model could help describe the contributing factors to regional differences beyond resource consumption and regional differences but would require incredibly granular data.

@@

Some regions appeared to produce many low quality grapes at scale whilst others focussed on producing higher quality grapes in lower volumes. This behaviour can also be observed when reviewing Wine Australia's annual reports, where it is apparent that some GI regions, such as the Riverland, are known for producing large amounts of lower grade grapes (grapes of lower value per tonne) \cite{wineaustraliaNationalVintageReport2022,winemakersfederationofaustraliaNationalVintageReport2017}. Comparatively other regions, such as Tasmania, only produce high quality/grade grapes but in much smaller quantities than the Riverland. The difference in pricing per tonne between the lowest and highest graded grapes can be greater a hundred times the difference in value per tonne.

@@

Not all regions target only one grade of grape, with some producing a variety of differently graded grapes; such as the Yarra Valley, which produces a variety of different grades of grapes, from C to A

@@

This effect could stifle the potential for market opportunities within lesser known regions. A further possibility is the existence of regional upper limits on potential quality, making the relationship between resource use and value have diminishing returns. Climate was considered to be a large determinant of the ability to grow a larger quantity of grapes, as well as a determinant in grape quality \citep{agostaRegionalClimateVariability2012}

% What is this below paragraph?
%The correlation between average sales price and yield was a negative trend (see table 2); the contributing factors to yield and average sales price was ???. Correlation values showed that water and emissions increased with yield but decreased with average sale price (see Table 4).
%
different strategies are likely employed between different regions, where some regions target the mass production of cheaper grapes over quality. This is most notable when grouping regions by climate, especially when considering GI Regions in the 'Hot Very Dry' climate (see Figure 7). The effect of climate in the models was not more significant than the more granular use of GI regions. The interaction between year and GI Region likely accounted for localised events such as bushfires, which would be impactful, but only at a local level in both time and space.

\subsection{Limitations}
Limitations included overestimating yield for models 1 and 2, (see Figures 1 and 2) and underestimating crop value in models 3 and 4 (see Figures 3 and 4).The issue of model 1 and 2 over predicting yield, may have been due to preventative measures brought on by regional pressures such as fire, frost and disease. Where, more resources were required to prevent these issues from spreading within a region, thus disproportionately effecting some vineyards compared to others locally. This type of maintenance is not well captured especially when considering that some regions, those in warmer areas are not as prone to disease as cooler climates and could potentially have lower operating costs per hectare. This could create a discrepancy in vineyards that utilise preventative measures in wetter regions, as opposed to those who do not, and thus expend less fuel and energy but risk disease. When reviewing the differences between regions it is important to consider that vineyards in Hot Very Dry areas can be hundreds of times the size of those in other regions. It is interesting that while area, although significantly correlated to the ratio of yield to area, was still lower than water and about the same as emissions. This points to economies of scale playing a role but still being only one consideration alongside the potential resources that can be used. The negative trend between size and average sales price could also be a side effect of mass supply verse demand, especially when looking at the level of difference in production of some vineyards (see Table 4). The relationships between yield, value and area are not simply about efficiently producing the most grapes; sales price and by association grape quality, are integral to the profitability, and this is strongly linked to resource-use and thus the longevity and sustainability of a vineyard.

In alternative attempts at models it was found that without the incorporation of GI Region or year the predictions greatly under performed. The possible reason behind this effect was that different strategies are likely employed between different regions, where some regions target the mass production of cheaper grapes over quality. % ALSO THAT CATASTROPHES HAPPEN EVEN ON SMALL SCALES THis needs to be tied up better.
%
%Models were compared using $R^2$ values. The comparison of models performance showed that the average price per tonne of grapes describes a great deal of the relationship between predictor and response when comparing Model 2 to Model 4 
% Graph of productivity verse value.
%(see Table \ref*{tab:modelperformance}). 
% This is important but you do not illustrate why
%
% This section needs to be heavily revised. Why are there tails on the distributions? What does a heavy tail indicate?
% What does it look like with respect to disaster events?
% split the discussion sections out of the results!! Even the questions I am asking are answered in the discussion, however they need to be highlighted as aspects of the models here beforehand.
Reviewing the data to uncover reasons for this included the use of binary variables such as the utilisation of renewable energy, contractors, and the occurrence of disease, fire and frost; however none of these variables were able to explain why some vineyards produced less, or why other vineyards sold at higher prices than predicted. A wide variety of these influences were likely already explained within the use of year and GI Region, or the interaction of both variables. The change between some regions was dramatic, with particularly warmer and drier regions producing much higher volumes of grapes at lower prices (See Figures 5 and 6). The use of other variables and methods, specifically splines, were able to create a more normally distributed set of residuals but at a drastically reduced accuracy when comparing R2 and RSE. The introduction of known average prices per tonne also helped increase R2 values a small amount; it is important to not that it is common practice for wineries to purchase grapes at a regional average rate, likely resulting in much less variance within a region.

Having more data for each region would also be an improvement, allowing greater comparison between regions. More variables may also help to discern vineyards that can produce larger volumes of grapes at higher prices. The use of semi transparent tools such as random forests and decision trees alongside more variables and data may help to uncover the reasons for values that were under or over estimated. These differences could be caused by the use of alternative sustainable practices in the field. While there is evidence to suggest that environmentally sustainable practices can reduce costs, increase efficiency, whilst improving the quality of grapes, more research is needed to link these benefits across different regions and climates \citep{baianoOverviewSustainabilityWine2021,marianiSustainableWinegrowingCurrent2015,montalvo-falconSustainabilityResearchWine2023}.

% This belongs in the discussion
The relationship between scope one emissions and the response variables that included average sales price

It is possible that the relationships between scope one emissions and the response variables were closely tied to a vineyards area. This possibility could be explained through the emissions

Noting that irrigation systems use fuel
and that the application of water was a significant variable in each model
scope one emissions' lack of significance and contribution given its F-statistics (See Tables 7 and 8),
 indicated that it is possible other vineyard activities requiring fuel are not as determining factors for a vineyards grape quality.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

There was an understandably strong relationship between size and resource use, with the overall space of a vineyard and its access to resources greatly determining the upper limit of potential yield. However, size was also inversely related to the potential quality, with higher quality being related to high resource inputs per area; rather than to the overall expenditure of resources. These effects were augmented by regional and yearly affects. Even given regional and yearly changes, there was a strong connection between smaller vineyards and higher quality. This could have been due to the easier management of smaller properties.

@@

 There are many on-the-ground decisions that influence both quality and yield. Comparing the $R^2$ values between Models 2 and 4 showed that the average price per tonne of grapes described a great deal of the relationship between resource use and yield when variables were considered as ratios of area (due to the discrepancy in $R^2$ between the two models, see Table \ref{tab:modelsummary}). This descrepency is likely due to different vineyard prioritisation, which can be described by the type of quality and quantity a vineyard aims to target. Decisions such as the prioritisation of quality over quantity, are governed by complex physical and social forces, for example: international market demands, disease pressures and natural disasters \citep{abadCoverCropsViticulture2021,cortezUsingDataMining2009,hallWithinseasonTemporalVariation2011,i.goodwinManagingSoilWater2009,kasimatiPredictingGrapeSugar2022,oliverReviewSoilPhysical2013,srivastavaNondestructiveSensingMethods2018}; with many of these occurrences being highlighted throughout the past decades vintage reports from Wine Australia \citep{wineaustraliaNationalVintageReport2019,wineaustraliaNationalVintageReport2021,wineaustraliaNationalVintageReport2022,winemakersfederationofaustraliaNationalVintageReport2013,winemakersfederationofaustraliaNationalVintageReport2014,winemakersfederationofaustraliaNationalVintageReport2015,winemakersfederationofaustraliaNationalVintageReport2016,winemakersfederationofaustraliaNationalVintageReport2017,winemakersfederationofaustraliaNationalVintageReport2018}. It is also important to consider that these reports show that the warm inland regions have seen a decline in profit during this period, whereas regions targetting quality did not. Size becomes an important consideration, as it dictates the potential capacity to produce greater volumes of grapes. However, given the comparison of value per area, regions with larger vineyards and larger vineyards in general, tend to underperform. When considering the 'Hot Very Dry' vineyards (see Figure \ref{fig:yield_vs_value_area}) These vineyards would be very competitive with only a minor increase to sale price, possibly outperforming other regions.
The negative trend between size and average sales price could be a side effect of supply verse demand, especially when looking at the level of difference in production of some vineyards. Economies of scale likely played a role in determining yield but were only one consideration alongside resource use. Size was also less of a determining factor when considering quality. It is possible that the relationship of scope 1 emissions between yield and quality was closely tied to a vineyard's area; due to requiring more fuel to cover issues (such as fixing a broken irrigation pipe), where  a larger area has the potential for issues to be further away. This is further cemented when noting that most irrigation systems are diesel based, with water use being a significant variable in each model and scope 1 emissions not; scope one emissions' lack of significance and contribution given its F-statistics, could be indicative that other vineyard activities requiring fuel are not as determining factors for a vineyards grape quality. The relationship between yield, value and area was not simply about efficiently producing the most grapes; sales price and by association grape quality, are integral to the profitability, and this is strongly linked to resource-use and thus the longevity and sustainability of a vineyard.
There are important considerations unique to winegrowing compared to other agricultural industries. The vertical integration of winegrowing within the wine industry ties winegrowers to secondary and tertiary industries, such as wine production, packaging, transport and sales. This results in unique issues and considerations for each vineyard, where on-the-ground decisions are influenced by other wine industry's choices, such as the use of sustainable practices in vineyards as a requirement for sale in overseas markets; notably these interactions can be further complicated by some winegrowers being completely integrated into a wine company, while others are not \citep{knightFirmResourcesDevelopment2019}. Incorporating decisions into the model could help describe the contributing factors to regional differences beyond resource consumption and regional differences but would require incredibly granular data and more sophisticated modelling.

@@

Some regions appeared to produce many low quality grapes at scale whilst others focussed on producing higher quality grapes in lower volumes. This behaviour can also be observed when reviewing Wine Australia's annual reports, where it is apparent that some GI regions, such as the Riverland, are known for producing large amounts of lower grade (low value per tonne) grapes \cite{wineaustraliaNationalVintageReport2022,winemakersfederationofaustraliaNationalVintageReport2017}. Comparatively other regions, such as Tasmania, only produce high quality/grade grapes but in smaller quantities. The difference in pricing per tonne between the lowest and highest graded grapes can be greater than a hundred times the difference in value per tonne.

@@

Not all regions target only one grade of grape, with some producing a variety of differently graded grapes; such as the Yarra Valley, which produces grades from C to A.

@@

This effect could stifle the potential for market opportunities within lesser known regions. A further possibility is the existence of regional upper limits on potential quality, or that there are diminishing returns in some regions when pursuing quality or quantity; however these types of relationships may be obfuscated by knowledgeable winegrowers who avoid this pitfall.
% What is this below paragraph?
%The correlation between average sales price and yield was a negative trend (see table 2); the contributing factors to yield and average sales price was ???. Correlation values showed that water and emissions increased with yield but decreased with average sale price (see Table 4).
Due to regional differences, different strategies are likely employed across different regions; such as some regions targeting mass production over quality. This is most notable when grouping regions by climate, especially when considering GI Regions in the 'Hot Very Dry' climate (see Figure \ref{fig:yield_vs_value}). In alternative attempts at models it was found that without the direct incorporation of GI Region or year, predictions greatly under performed. The effect of climate in the models was never as significant as the more granular GI regions, and always led to less accurate models. Although not chosen over GI region, climate was considered to be a large determinant of the ability to produce larger quantities of grapes, as well as a determinant in grape quality \citep{agostaRegionalClimateVariability2012}. The more granular GI Region likely explained a broader mix of geographical phenomenon, such as soil, geology and access to water resources \citep{abbalDecisionSupportSystem2016,carmonaUseParticipatoryObjectOriented2011}. The interaction between year and GI Region likely accounted for events such as bushfires, which would be impactful, but only at a local level, both in time and space.

\subsection{Limitations}
Limitations included overestimating yield for models 1 and 2, and underestimating crop value in models 3 and 4 (see appendix). The issue of model 1 and 2 over predicting yield, may have been due to preventative measures brought on by regional pressures such as fire, frost and disease. Where, more resources were required to prevent these issues from spreading within a region, thus disproportionately effecting some vineyards compared to others locally. This type of maintenance is not well captured especially when considering that some regions, especially those in warmer areas, are not as prone to disease as cooler climates and could potentially have lower operating costs per hectare. This could create a discrepancy in vineyards that utilised preventative measures in wetter regions, as opposed to those that did not, thus expending less fuel and energy but risking disease. When reviewing the differences between regions it is important to consider that vineyards in 'Hot Very Dry' areas can be hundreds of times the size of those in other regions. This limitation could be overcome by incorporating the profitability of vineyards, compare the financial success of working at different operational scales.
\newline
 %The possible reason behind this effect was that different strategies are likely employed between different regions, where some regions target the mass production of cheaper grapes over quality. % ALSO THAT CATASTROPHES HAPPEN EVEN ON SMALL SCALES THis needs to be tied up better.
%Reviewing data to uncover reasons for the disparity between production and quality of similar vineyards  included the use of 
Variables such as the utilisation of renewable energy, contractors, and the occurrence of disease, fire and frost were originally explored to capture the discrepancies between similar vineyards that produced different  yields and crop values. However, none of these variables were significantly connected to the response variables, and did not add to model accuracy; even when considered as interactions. The use of other methods, specifically splines, resulted in more normally distributed residuals but at a drastically reduced overall accuracy when comparing $R^2$ and Residual Square Error. Attempts to fully explain small variations was always overshadowed by the dramatic differences in regional trends.
\newline
Having more data for each region would also be an improvement, allowing greater comparison between regions. More variables may also help to discern vineyards that can produce larger volumes of grapes at higher prices. The use of semi transparent tools such as random forests and decision trees alongside more variables and data may help to uncover the reasons for values that were under or overestimated. These differences could be caused by the use of alternative sustainable practices in the field. And, while there is evidence to suggest that environmentally sustainable practices can reduce costs, increase efficiency, whilst improving the quality of grapes; more research is needed to link these benefits across different regions and climates \citep{baianoOverviewSustainabilityWine2021,marianiSustainableWinegrowingCurrent2015,montalvo-falconSustainabilityResearchWine2023}.
\section{Conclusion}
% This belongs in the discussion
